### 2021-11-03 paper/manuscript.Rmd
fix latex

$\theta_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + ⋯ + \beta_{p}x_{p}+ \zeta_{i}$			(6)

@@

$y_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + ⋯ + \beta_{p}x_{p}+ \zeta_{i} + \varepsilon_{i}$			(7)

@@

To determine the effect of the design factors on predictive performance $R^2$ of all algorithms, four separate ANOVA’s were performed. The effect size $η^{2}$ per condition per algorithm, including interactions can be found in table 1. Do note that the ANOVA's were performed with the normality assumption violated. The estimates serve as a guidance, rather than an non-contestable result.

Not too surprisingly, It was found that the true effect size $β$ had the largest effect on the predictive $R^{2}$ for all algorithms. As $\beta$ increased, the performance of all algorithms increased as well. However, $\beta$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model. The image of the interaction is shown in image 1. For the exponential and cubic model, the increase of $R^{2}$ slows for every higher value for $\beta$. The two-way interaction model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $\beta$ increases from 0.2 to 0.4. Also noteworthy is that the cubic model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing. There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while MetaForest performed worst.

@@

*Estimating residual heterogeneity* ($τ^{2}$)
The ability of the algorithms to correctly estimate $τ^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms. Again, the median and MAD were used as metrics for performance. The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the Metaforest algorithm $\Delta\tau^2_{MF} = 0.09 \pm 0.13$. The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{hs} = 0.23 \pm 0.17$. The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it. One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased. This implies that there is more variation in performance as median performance worsens.

@@

The estimated model had one of the biggest effect on the correct estimation of $τ^{2}$. This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains cubic relationships. Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ . It becomes more clear why this overestimation occurs when showing the interaction between the effect size and the model estimated on $\Delta\tau^{2}$ shown in image 9. First note the general trend which seems to be that for all models, except the linear, $\tau^{2}$ gets more overestimated the higher the true effect size is. This is not the case for the linear algorithm, where the effect of $\beta$ on $\Delta\tau^{2}$  seems close to zero, except for MetaForest. However, note the scales for the y-axes. While the interaction, linear and stay well within a confined interval, the algorithms severely overestimate $\tau^{2}$ when the model contains cubic terms. Especially Metaforests overestimation is substantial when $\beta$ = 0.8 and the estimated model is cubic with $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$, although all other algorithms also have a $\Delta\tau^{2} > 1$ in these conditions. Interestingly, the Pema algorithms even outperform the RMA algorithm within these conditions. The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10. MetaForest seems most affected by the increase in $\beta$, but in general performs better than the Pema algorithms when $\beta$ < 0.8. The RMA algorithm performs best overall.

>>>>

$\theta_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p}+ \zeta_{i}$			(6)

@@

$y_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p}+ \zeta_{i} + \varepsilon_{i}$			(7)

@@

To determine the effect of the design factors on predictive performance $R^2$ of all algorithms, four separate ANOVA’s were performed. The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 1. Do note that the ANOVA's were performed with the normality assumption violated. The estimates serve as a guidance, rather than an non-contestable result.

Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on the predictive $R^{2}$ for all algorithms. As $\beta$ increased, the performance of all algorithms increased as well. However, $\beta$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model. The image of the interaction is shown in image 1. For the exponential and cubic model, the increase of $R^{2}$ slows for every higher value for $\beta$. The two-way interaction model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $\beta$ increases from 0.2 to 0.4. Also noteworthy is that the cubic model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing. There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while MetaForest performed worst.

@@

*Estimating residual heterogeneity* ($\tau^{2}$)
The ability of the algorithms to correctly estimate $\tau^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms. Again, the median and MAD were used as metrics for performance. The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the Metaforest algorithm $\Delta\tau^2_{MF} = 0.09 \pm 0.13$. The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{hs} = 0.23 \pm 0.17$. The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it. One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased. This implies that there is more variation in performance as median performance worsens.

@@

The estimated model had one of the biggest effect on the correct estimation of $\tau^{2}$. This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains cubic relationships. Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ . It becomes more clear why this overestimation occurs when showing the interaction between the effect size and the model estimated on $\Delta\tau^{2}$ shown in image 9. First note the general trend which seems to be that for all models, except the linear, $\tau^{2}$ gets more overestimated the higher the true effect size is. This is not the case for the linear algorithm, where the effect of $\beta$ on $\Delta\tau^{2}$  seems close to zero, except for MetaForest. However, note the scales for the y-axes. While the interaction, linear and stay well within a confined interval, the algorithms severely overestimate $\tau^{2}$ when the model contains cubic terms. Especially Metaforests overestimation is substantial when $\beta$ = 0.8 and the estimated model is cubic with $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$, although all other algorithms also have a $\Delta\tau^{2} > 1$ in these conditions. Interestingly, the Pema algorithms even outperform the RMA algorithm within these conditions. The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10. MetaForest seems most affected by the increase in $\beta$, but in general performs better than the Pema algorithms when $\beta$ < 0.8. The RMA algorithm performs best overall.
